---
title: "Exercises"
output: html_document
---

Exercise 3.2 From concerts_obo,

Retrieve the 3rd and 5th concert observations and bind the result value with an object name concerts_sampled.

For the second concert, what are its first show’s time and location? Retrieve the information and bind the value with firstShowInfo.

```{r}
concerts_sampled <- concerts_obo[c(3,5)] 

firstShowInfo <- concerts_obo[[2]][["showInfo"]][[1]][c("time","location")]
```


Exercise 3.3 From concerts_obo, due to Covid-19 the 3rd concert’s 1st show time is changed to “2022/01/31 19:30:00” and the location is changed to “Taichung Opera House”, please change the information

```{r}
concerts_obo[[3]]$"showInfo"[[1]][c("time","location")] <- list("time" = "2022/01/31 19:30:00","location" = "Taichung Opera House")
```


Exercise 3.4 How do you add the new born if you use JohnsFamilyCopy3$children[3]:

```{r}
# name: "John"  
# age: 3
list(
  list(
    name="John",
    age=3
    )
  )
```

```{r}
# Therefore, the value of child 3 should follow that same structure
JohnsFamilyCopy3 <- JohnsFamily
JohnsFamilyCopy3$children[3] <- 
  list(
    list(
      name="Lisa",
      age=0
    )
  )
```

Exercise 3.5 The 5th concert decides to add one more show which shares the same show information as its first show except the date is 2 days later.

```{r}
concerts_obo[[5]]$showInfo[[2]] <- concerts_obo[[5]]$showInfo[[1]]
concerts_obo[[5]]$showInfo[[2]][c(1, 8)] <- list(time="2021/12/20 10:00:00", endTime="2021/12/21 22:00:00")
```







