---
title: "Midterm"
output: html_document
---
## The Question

# 1 Econ Survey

An online survey is distributed to students of Economics department. 

## 1.1 Storing questions

There are two questions:

  * question 1: "Are you happy with our campus? Choose a number from 5(very happy), 4(happy), 3(satisfy), 2( unhappy), to 1(very unhappy)." 
  
  * question 2: "Did you participate in any of the following activities? Check all that apply to you. (student association, school club, school sport team, department sport team)"

Suppose the following retrieval will print each question respectively: 
```{r}
survey$questions[[1]] # will show as
"Are you happy with our campus? Choose a number from 5(very happy), 4(happy), 3(satisfy), 2( unhappy), to 1(very unhappy)."
survey$options[[1]] # will show as
c(1, 2, 3, 4, 5)
survey$questions[[2]] # will show as
"Did you participate in any of the following activities? Check all that apply to you. (student association, school club, school sport team, department sport team)"
survey$options[[2]] # will show as
c("student association", "school club", "school sport team", "department sport team")
```

Construct the `survey` object that can satisfy the above retrieval outcomes:
```{r ans11}
# declare then add method
survey <- list() # declare
survey$questions[[1]] <- "Are you happy with our campus? Choose a number from 5(very happy), 4(happy), 3(satisfy), 2( unhappy), to 1(very unhappy)." # then-add
survey$options[[1]] <- c(1, 2, 3, 4, 5)
survey$questions[[2]] <- "Did you participate in any of the following activities? Check all that apply to you. (student association, school club, school sport team, department sport team)"
survey$options[[2]] <- c("student association", "school club", "school sport team", "department sport team")
# survey
```

## 1.2 One observation

One student's response is

  * question 1: 4
  
  * question 2: "school club" and "department sport team"

Construct an object named `single_response` whose structure satisfies the following requirements:  
```{r}
choice1 <- single_response$questions[[1]]
survey$options[[1]][[choice1]] # will show as
c(1, 2, 3, 4, 5)[[choice1]] # will show as
4 # therefore, choice <- 4
# therefore, 
single_response$questions[[1]] # will show as
4

choice2 <- single_response$questions[[2]]
survey$options[[2]][choice2] # will show as
c("student association", "school club", "school sport team", "department sport team")[choice2]
c("student association", "school club", "school sport team", "department sport team")[c(2, 4)]
c("school club", "department sport team")

# Therefore, choice2 <- c(2, 4)
# Therefore, single_response$questions[[2]] also show c(2, 4)
```


```{r ans12}
single_response <- list() # declare
single_response$questions[[1]] <- 4
single_response$questions[[2]] <- c(2, 4)
# single_response
```

## 1.3 Several observations

```{r}
list(
  questions = list(
    c(4),
    c(2, 4)
  )
)
```

There are three students responded to the survey. Their choices are

```{r}
c("student association", "school club", "school sport team", "department sport team")
```

  * student 1: Q1 choose 4; Q2 choose "school club" and "department sport team"  
  
```{r}
list(
  questions=list(4, c(2,4))
)
```
  
  * student 2: Q1 choose 3; Q2 does not answer (missing value record NA)
  
```{r}
list(
  questions=list(3, NA)
)
```
  
  * student 3: Q1 choose 5; Q2 choose "student association", "school club", "school sport team"
  
```{r}
list(
  questions=list(5, c(1, 2, 3))
)
```

Store three responses in `responses` object so that for `i=1`
```{r}
i=1
survey$options[[1]][
  responses[[i]]$questions[[1]]
] # show student i's chosen option from question 1 as
4
survey$options[[2]][
  responses[[i]]$questions[[2]]
] # show student i's chosen options from question 2 as
c("school club", "department sport team")
```

```{r ans13}
responses <- list(
  list(
    questions=list(
      c(4), c(2, 4) 
    )
  ),
  list(
    questions=list(
      c(3), c(NA)
    )
  ),
  list(
    questions=list(
      c(5), c(1, 2, 3)
    )
  )
)
# responses
```

## 1.4 Modify 

Modify `responses` so that:

  * student 2's response is removed completely
```{r}
responses[[2]] <- NULL
```
  
  * student 1 and 3's response to question 1 are all changed to 3
```{r}
responses[[1]]$questions[[1]] <- 3
responses[[3]]$questions[[1]] <- 3
```
  
  
```{r ans14}
# version 1
responses[[2]] <- NULL
responses[[1]]$questions[[1]] <- 3
responses[[2]]$questions[[1]] <- 3 # because [[2]] had been deleted
```

```{r ans14}
# version 2
responses[[1]]$questions[[1]] <- 3
responses[[3]]$questions[[1]] <- 3
responses[[2]] <- NULL
# responses
```

## 1.5 Feature by feature
`responses` from the previous question is an observation-by-observation data set. We want to construct a feature-by-feature data set. The feature names are:

  * question1, question2.student_association, question2.school_club, question2.school_sport_team, question2.department_sport_team.

For question2.XXX features, their values are logical. TRUE means the student has participated in activity XXX; FALSE means has not. Please construct a feature-by-feature list data set for those three students based on their 1.3 answers, and save the data set to object `responses_fbf`

```{r ans15}
responses_fbf <-
  list(
    question1 = c(4, 3, 5), 
    question2.student_association = c(F, NA, T), 
    question2.school_club = c(T, NA, T), 
    question2.school_sport_team = c(F, NA, T),
    question2.department_sport_team = c(T, NA, F)
  )
# responses_fbf
```
