---
title: "Week 9 class & factor class"
output: html_document
---

##class

```{r}
typeof(c("John", "Mary"))
typeof(c(2, 3.1412))
typeof(c(TRUE, TRUE, F))
```

```{r}
class(c("John", "Mary"))
class(c(2, 3.1412))
class(c(TRUE, TRUE, F))
```

**class** is a categorization method that categorizes different values based on **what we can do with those values**.

  * type: man and woman
  * class: difference based on skills. (plumber class, teacher class)
  
***

```{r}
# date time information
dateTimeInfo <- "2021-01-01 12:03:33"
typeof(dateTimeInfo)
```

```{r}
class(dateTimeInfo)
```

```{r}
dateTimeInfo + 20
# character class value + 20
```

 we can choose proper parsing function to teach R understand a date time value is more than a character--teach R understand a class called date/time.

```{r}
dateTimeInfo2 <- lubridate::ymd_hms("2021-01-01 12:03:33")
class(dateTimeInfo2)
```

  * lubridate::ymd_hms is a parsing function tp teach R understand date time.

```{r}
dateTimeInfo2 + lubridate::seconds(20)
```

type: how we store **raw** information
class: what we (R) can do with different information

## factor_class

```{r}
commonClasses <- list()
```

  * declare-then-add method to create a vector.

```{r}
# save three different atomic vectors
commonClasses$character <- c("John", "Mary", "Bill")
commonClasses$numeric <- c(2.3, 4, 7)
commonClasses$logical <- c(TRUE, T, F, FALSE)
```

```{r}
# check each atomic vector class
class(commonClasses$character) # name call on commonClasses to get its value then retrieve the element value whose element name is "character"

class(commonClasses$numeric)
class(commonClasses$logical)
```

```{r}
bloodTypes <- c("AB", "AB", "A", "B", "A", "A", "B", "O", "O", "AB")
```

```{r}
bloodTypes_fct <- 
  factor(bloodTypes)
# after name call on bloodTypes
  factor(
    c("AB", "AB", "A", "B", "A", "A", "B", "O", "O", "AB")
  )
```

```{r}
table(bloodTypes_fct)
```

```{r}
table(bloodTypes)
```

```{r}
levels(bloodTypes_fct)
```

```{r}
levels(bloodTypes)
```

```{r}
bloodTypes_fct_levelsSetup <- 
  factor(bloodTypes, levels=c("A", "B", "O", "AB"))
```

```{r}
class(bloodTypes_fct_levelsSetup)
```

```{r}
table(bloodTypes_fct_levelsSetup)
```

***

```{r}
household_income <- c("low income", "low income", "middle income", "low income", "high income", "middle income", "high income", "high income", "middle income", "middle income")
```

  * low income < middle income < high income

```{r}
household_income_fct <- 
  factor(household_income)
levels(household_income_fct)
```

```{r}
table(household_income_fct)
```

```{r}
household_income_fct_levelsSetup <-
  factor(household_income, levels = c("low income", "middle income", "high income"))
levels(household_income_fct_levelsSetup)
```

```{r}
table(household_income_fct_levelsSetup)
```

```{r}
household_income_fct_levelsSetup[[1]] # low income
```

```{r}
household_income_fct_levelsSetup[[1]] < "middle income"
```

```{r}
household_income_fct_levelsSetup_ordered[[1]] < "middle income"
```

  * human would say yes, it is true.

```{r}
household_income_fct_levelsSetup[[1]] > "low income"
```

```{r}
household_income_fct_levelsSetup_ordered[[1]] > "low income"
```

  * human would no, it is not true (false)

```{r}
household_income_fct_levelsSetup_ordered <-
  factor(
    household_income, 
    levels = c("low income", "middle income", "high income"),
    ordered = T # Is levels ordered? (from the smallest to the largest)
    )
```

```{r}
class(household_income_fct_levelsSetup_ordered)
```

```{r}
class(household_income_fct)
class(household_income_fct_levelsSetup)
```

```{r}
commonClasses$ordered_factor <- household_income_fct_levelsSetup_ordered
class(commonClasses$ordered_factor)
```

```{r}
commonClasses$factor <-
bloodTypes_fct_levelsSetup
class(commonClasses$ordered_factor)
# factor parsed data has factor class
```




